---
title: "Original Homework Code"
author: "Christian Gagnon"
date: "9/16/2019"
output: html_document
---
***

# Homework 02

***

This is the code for [homework 02](https://fuzzyatelin.github.io/bioanth-stats/homework-02.html), on week three of AN597. This id homewrok linked to module 6 and 7.

>Every Saturday morning, at the same time, a primatologist goes and sits in the forest to listen for titi monkey calls, counting the number of calls they hear in a 2 hour window from 5am to 7am. Based on previous knowledge, she believes that the mean number of calls she will hear in that time is exactly 15. Let X represent the appropriate Poisson random variable of the number of calls heard in each monitoring session.

Question 1: What is the probability that she will hear more than 8 calls during any given session?
```{r}
1-ppois(8,15)
```

Question 2: What is the probability that she will hear no calls in a session?
```{r}
ppois(0,15)
```

Question 3:What is the probability that she will hear exactly 3 calls in a session?
```{r}
ppois(3,15)-ppois(2,15)
```


Question 4: Plot the relevant Poisson mass function over the values in range 0 ≤ x ≤ 30.
```{r}
x <- 0:30
l = 15
probset<-dpois(x=x,lambda=l)
barplot(probset,names.arg=x,space=0,xlab="x",ylab="Pr(X = x)",main="Probability Mass Function")
```

Question 5: Simulate 104 results from this distribution (i.e., 2 years of Saturday monitoring sessions).
```{r}
y<-rpois(104,15)
y
```


Question 6: Plot the simulated results using hist() and use xlim() to set the horizontal limits to be from 0 to 30. How does your histogram compare to the shape of the probability mass function you plotted above?
```{r}
hist(y,xlim=c(0,30),xlab="Number of Calls",main="Call Monitoring Histogram",breaks=30,col="aquamarine")
```

## Challenges

<ol>
<li>Conceptualizing the problem we were given</li>
<li>Couldn't figure out the right function to get the probilities for a poisson distribution.</li>
<li>How to get the probability for an exact number.</li>
<li>xlim variable for the historgram.</li>
<li>How to show individual histogram bars for each possible result.</li>
</ol>

